Verification of OpenSSL's SHA3 Keccak function using the Software Analysis Workbench

### 2021-11-22 paper/introduction.tex
Revise to use LLNCS formating for NFM Submission

\section{Introduction}\label{sec:introduction}
  The Secure Hashing Algorithm (SHA) family of cryptography is widely used as a means of providing increased security through generating/verifying digital signatures, deriving keys, and generating pseudorandom bits (\href{https://csrc.nist.gov/publications/detail/fips/202/final}{NIST specification}).  
  The structure and computations of these algorithms is defined by NIST in mathematical specifications.  
  Because these specifications are just figures on a page, any assurance of correctness of an algorithm’s implementation is dependent on a visual review of the code coupled with a small sampling of test vectors.

>>>>

  The Secure Hashing Algorithm (SHA) family of cryptography is widely used as a means of providing increased security through generating/verifying digital signatures, deriving keys, and generating pseudorandom bits (\href{https://csrc.nist.gov/publications/detail/fips/202/final}{NIST specification}).  
  The structure and computations of these algorithms is defined by NIST in mathematical specifications.  
  Because these specifications are just figures on a page, any assurance of correctness of an algorithm’s implementation is dependent on a visual review of the code coupled with a small sampling of test vectors.

### 2021-11-22 paper/openssl.tex
Revise to use LLNCS formating for NFM Submission

\section{SHA3 OpenSSL in Cryptol}\label{sec:openssl}
Even with the highly modular approach of the SHA3 algorithm, a direct proof from the Cryptol specification that matched the NIST standard and the OpenSSL source code was unviable.
OpenSSL's source code is often used in low-level software, and it is often optimized to improve performance and viability for embedded systems.
One major instance of such optimization proved significant enough to prevent a direct proof from the NIST Cryptol specification to OpenSSL.

>>>>

Even with the highly modular approach of the SHA3 algorithm, a direct proof from the Cryptol specification that matched the NIST standard and the OpenSSL source code was unviable.
OpenSSL's source code is often used in low-level software, and it is often optimized to improve performance and viability for embedded systems.
One major instance of such optimization proved significant enough to prevent a direct proof from the NIST Cryptol specification to OpenSSL.

### 2021-11-22 paper/paper.tex
Add outline
Revise to use LLNCS formating for NFM Submission

%%
%% This is file `sample-sigplan.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigplan')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigplan.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan, 10pt, anonymous, review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\usepackage{subcaption}
\usepackage{paralist}
\usepackage{color}
\definecolor{blue}{RGB}{42,0,255}
\definecolor{green}{RGB}{63,127,95}
\definecolor{purple}{RGB}{127,0,85}
\definecolor{lime}{RGB}{114, 148, 0}
\usepackage{listings}
\lstdefinelanguage{Cryptol}{
  keywordstyle=[1]\color{blue}\bfseries,
  keywordstyle=[2]\color{purple}\bfseries,
  keywordstyle=[3]\color{black}\bfseries,
  basicstyle={\color{lime}\scriptsize},
  literate=*
  {*}{{{\color{black}$*$}}}{1}
  {=}{{{\color{black}=}}}{1}
  {+}{{{\color{black}+}}}{1}
  {-}{{{\color{black}$-$}}}{1}
  {\%}{{{\color{black}\%}}}{1}
  {(}{{{\color{black}(}}}{1}
  {)}{{{\color{black})}}}{1}
  {\{}{{{\color{black}\{}}}{1}
  {\}}{{{\color{black}\}}}}{1}
  {[}{{{\color{black}[}}}{1}
  {]}{{{\color{black}]}}}{1}
  {|}{{{\color{black}$|$}}}{1}
  {>}{{{\color{black}$>$}}}{1}
  {<}{{{\color{black}$<$}}}{1}
  {\#}{{{\color{black}\#}}}{1}
  {@}{{{\color{black}@}}}{1}
  {.}{{{\color{black}.}}}{1}
  {\'}{{{\color{black}'}}}{1}
  {:}{{{\color{black}:}}}{1}
  {^}{{{\color{black}$\char`\^$}}}{1}
  {&}{{{\color{black}\textbackslash}}}{1},
  morekeywords=[1]{Bit, Integer, STATE_ARR, W, COL, type, LIST4, LIST63, True, False},
  morekeywords=[2]{if, then, else, where},
  morekeywords=[3]{pi, rc, cond, a, b, x, y, z, for, n, r, R, f, rs, i, index, t, 
    vals, loop, state, while, take}
}

@@

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Verification of OpenSSL's SHA3 Keccak function using the Software Analysis Workbench}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Benjamin Winters}
\author{Parker Hanson}
\author{Eric Mercer}
\email{egm@cs.byu.edu}
\orcid{0000-0002-2264-2958}
\author{Brett Decker}
\email{bdecker@cs.byu.edu}
\affiliation{%
  \institution{Brigham Young University}
  \streetaddress{3365 TMCB}
  \city{Provo}
  \state{Utah}
  \country{USA}
  \postcode{84602}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.

%%
%% The abstract is a short summary of the work to be presented in the
%% article.

\input{abstract}

%%NEED TO COMPLETE THIS BEFORE SUBMISSION
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{verification, cryptography, symbolic execution, SHA3}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
% \begin{teaserfigure}
%   \includegraphics[width=\textwidth]{sampleteaser}
%   \caption{Seattle Mariners at Spring Training, 2010.}
%   \Description{Enjoying the baseball game from the third-base
%   seats. Ichiro Suzuki preparing to bat.}
%   \label{fig:teaser}
% \end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\input{introduction}
%%\input{preliminaries}
\input{proof}
\input{fips}
\input{openssl}
\input{results}
\input{related}
\input{conclusion}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}

\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

\end{document}
\endinput
%%
%% End of file `paper.tex'.

>>>>

\documentclass[runningheads]{llncs}
%
\usepackage{paralist}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{color}
\definecolor{blue}{RGB}{42,0,255}
\definecolor{green}{RGB}{63,127,95}
\definecolor{purple}{RGB}{127,0,85}
\definecolor{lime}{RGB}{114, 148, 0}
\usepackage{listings}
\lstdefinelanguage{Cryptol}{
  keywordstyle=[1]\color{blue}\bfseries,
  keywordstyle=[2]\color{purple}\bfseries,
  keywordstyle=[3]\color{black}\bfseries,
  basicstyle={\color{lime}\scriptsize},
  literate=*
  {*}{{{\color{black}$*$}}}{1}
  {=}{{{\color{black}=}}}{1}
  {+}{{{\color{black}+}}}{1}
  {-}{{{\color{black}$-$}}}{1}
  {\%}{{{\color{black}\%}}}{1}
  {(}{{{\color{black}(}}}{1}
  {)}{{{\color{black})}}}{1}
  {\{}{{{\color{black}\{}}}{1}
  {\}}{{{\color{black}\}}}}{1}
  {[}{{{\color{black}[}}}{1}
  {]}{{{\color{black}]}}}{1}
  {|}{{{\color{black}$|$}}}{1}
  {>}{{{\color{black}$>$}}}{1}
  {<}{{{\color{black}$<$}}}{1}
  {\#}{{{\color{black}\#}}}{1}
  {@}{{{\color{black}@}}}{1}
  {.}{{{\color{black}.}}}{1}
  {\'}{{{\color{black}'}}}{1}
  {:}{{{\color{black}:}}}{1}
  {^}{{{\color{black}$\char`\^$}}}{1}
  {&}{{{\color{black}\textbackslash}}}{1},
  morekeywords=[1]{Bit, Integer, STATE_ARR, W, COL, type, LIST4, LIST63, True, False},
  morekeywords=[2]{if, then, else, where},
  morekeywords=[3]{pi, rc, cond, a, b, x, y, z, for, n, r, R, f, rs, i, index, t, 
    vals, loop, state, while, take}
}

@@

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Verification of OpenSSL's SHA3 Keccak function using the Software Analysis Workbench}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
  Parker Hanson\inst{1} \and
  Benjamin Winters\inst{1} \and
  Eric Mercer\inst{1}\orcidID{0000--0002-2264-2958} \and
  Bret Decker\inst{1}
}
%
\authorrunning{P. Hanson et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
  Brigham Young University, Provo UT 84602, USA
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{abstract}
\keywords{verification \and cryptography \and symbolic execution \and SHA3.}
\end{abstract}

\section{Introduction}\label{sec:introduction}
\input{introduction}

%%\input{preliminaries}

\section{Proof Overview and Results}\label{sec:proof}
\input{proof}

\section{SHA3 FIPS Specification in Cryptol}\label{sec:fips}
\input{fips}

\section{SHA3 OpenSSL in Cryptol}\label{sec:openssl}
\input{openssl}

\section{Results and Discussion}\label{sec:results}
\input{results}

\section{Related Work}\label{sec:related}
\input{related}

\section{Conclusion}\label{sec:conclusion}
\input{conclusion}

%
%
%
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{paper}
%
\end{document}
